\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\setcounter{page}{1}
\pagenumbering{arabic}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{enumerate}
\usepackage[dvips]{graphicx,epsfig}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{srcltx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[british]{babel}
\usepackage[mmddyyyy]{datetime}
\usepackage{hyperref}
\renewcommand{\baselinestretch}{1.2}

\marginparwidth=0in \marginparsep=0in \oddsidemargin=0in \evensidemargin=0in \headheight=0in \headsep=0in \topmargin=0.5in \textheight=9in
\textwidth=6in 
\setlength{\parindent}{0pt}

\begin{document}

\begin{tabular}{l r}
University of Essex  \hspace{35ex}& Session 2024-2025 \\
Department of Economics \hspace{35ex} & Autumn Term\\
Dr. Neslihan Sakarya \hspace{35ex} &
\end{tabular}
\\
\begin{center}
\large{\textbf{EC466: Estimation and Inference in Econometrics}\\
Exercise \# 1}
\end{center}
\vspace*{0.5cm}
You need to install Matlab on your computer to solve Question 1. To install Matlab please go to \url{https://software.essex.ac.uk/} and download matlab.exe file. Matlab will ask you to choose which toolboxes you need to install. You do not need to install any extra toolboxes other than the necessary ones. The necessary toolboxes will be automatically checked by Matlab. Note that it might take an hour to install matlab on your computer. So ensure that you start your homework at least 3 days before the deadline.

\begin{enumerate}
\item{Please answer the first 15 questions on EC$466$ex1.m {\bf OR} EC$466$hw1.mlx. The first file is a matlab script file, the second one is a matlab live script file. If you are not familiar with Matlab please see the first 6 minutes of the following video on Youtube \url{https://www.youtube.com/watch?v=zr_aB7V79DE}. Please copy and paste {\bf attend.xls} file on the Matlab folder; otherwise, Matlab will give you the following error ``{\color{red}Error using xlsread (line 136)
XLSREAD unable to open file 'attend.xls'.
File '/Users/sakarya/Dropbox/Sakarya-Kotan/derivation/attend.xls' not found.}" For instance, I saved {\bf attend.xls} file in the following folder \linebreak ``/Users/sakarya/Documents/MATLAB".}
\item{Show that ${\bf X'X}$ is a symmetric positive definite matrix.}
\item{Show that $({\bf X'X})^{-1}$ is a symmetric positive definite matrix.}
\vspace*{0.5cm}
\end{enumerate}
\textbf{Please upload your solutions as well as a copy of your Matlab output on Moodle by Tuesday, October 29 at 23:59.}

\end{document}