\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\setcounter{page}{1}
\pagenumbering{arabic}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{enumerate}
\usepackage[dvips]{graphicx,epsfig}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{srcltx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[british]{babel}
\usepackage[mmddyyyy]{datetime}
\usepackage{hyperref}
\renewcommand{\baselinestretch}{1.2}

\marginparwidth=0in \marginparsep=0in \oddsidemargin=0in \evensidemargin=0in \headheight=0in \headsep=0in \topmargin=0.5in \textheight=9in
\textwidth=6in 
\setlength{\parindent}{0pt}

\begin{document}

\begin{tabular}{l r}
University of Essex  \hspace{35ex}& Session 2024-2025 \\
Department of Economics \hspace{35ex} & Autumn Term\\
Dr. Neslihan Sakarya \hspace{35ex} &
\end{tabular}
\\
\begin{center}
\large{\textbf{EC466/966: Estimation and Inference in Econometrics}\\
Exercise \# 3}
\end{center}

\begin{enumerate}
\item{Please answer the questions on EC$966\_466$hw3.m {\bf OR} EC$466\_966$hw3.mlx. The first file is a matlab script file, the second one is a matlab live script file. Please copy and paste {\bf hprice.xls} file in the Matlab folder on your computer.}
\item{Suppose that you have the following regression model}
\begin{align*}
{\bf y}={\bf X}\beta +\epsilon,
\end{align*}
where ${\bf y}$ is the $n \times 1$ vector of the dependent variable, ${\bf X}$ is the $n \times K$ vector of regressors, $\beta$ is the $K \times 1$ vector of the model parameters, and $\epsilon$ is the $n \times 1$ vector of the error term. Assume that Classical Linear Regression Model assumptions hold except the homoskedasticity assumption, i.e., $E(\epsilon \epsilon'|{\bf X})={\bf V}$ where ${\bf V}$ is a symmetric and positive definite matrix, and is a function of ${\bf X}$. 
\begin{enumerate}
\item{Derive the Generalized Least Squares (GLS) estimator.}
\item{Show that the GLS is an (conditionally) unbiased estimator.}
\item{Derive the variance-covariance matrix for the GLS estimator.}
\item{Is the OLS estimator unbiased in the presence of heteroskedasticity?}
\end{enumerate}
\vspace*{0.5cm}
\end{enumerate}
\textbf{Please upload your solutions and  Matlab script files on Moodle until November 12, Thursday 23:59.}

\end{document}